Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2019-01-18 ms5n17-tlp-mn-180216-001.tex
Final version MS

Microfluidic NMR (Nuclear Magnetic Resonance) can probe chemical or bio-chemical reactions, including the metabolism of cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment. We present a dual-channel modular probe assembly for  high efficiency microfluidic-NMR. The samples are contained in exchangeable, flow compatible planar microfluidic devices. The detector including the tuning and matching circuitry of the probe is modular and allows the use of different detectors optimised for different experimental conditions on the same probe base. The complete probe can be built from easily available parts. The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit board) materials. The probe has a limit of detection of 1.18 nmol s$^{-1/2}$, resolution of 3.35 Hz and, excellent B$_{1}$ homogeneity. The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel (\textsuperscript{13}C or \textsuperscript{15}N) frequencies. We have successfully acquired \textsuperscript{1}H-\textsuperscript{13}C and \textsuperscript{1}H-\textsuperscript{15}N heteronuclear correlation spectrum (HSQC). Particularly, \textsuperscript{1}H-\textsuperscript{15}N HSQC spectrum of 1 mM \textsuperscript{15}N labeled ubiquitin from 2.5 $\mu$l of sample volume.

@@

in the culture of cells, cell aggregates, and small organisms. 

@@

throughput~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}. 

@@

NMR spectroscopy can provide a useful complementary readout capability 
for microfluidic devices. For example, the metabolic activity of cell cultures 
can be followed non-invasively by NMR throughout the course of the experiment, 
while effects on cell differentiation can still be analysed by a (destructive) 
transcriptomic analysis at the end. Unfortunately, the sensitivity 
of NMR is much lower than that of optical techniques. 
The small volumes involved in microfluidic systems
 (typically in the range of 1~$\mu$l) 
compound this problem. As is well known, the mass limit of detection of 
inductive NMR detectors improves as they are scaled down~\cite{Olson1995}. 
On this basis, a number of different micro-NMR detector designs have been 
proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. 
In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, 
planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline 
detectors~\cite{stripline_jan}. 
Significant research has gone into developing micro-NMR detectors for flow probes, 
where the sample container takes the form of a fixed capillary into which the sample
must be injected. Only a few designs that allow insertion of a removable microfluidic 
device into the detector have been described~\cite{Spengler-2014,Spengler-2016,gream_2016}.

In this paper we present a novel modular probe designed for generic 
microfluidic-NMR experiments. The design is based on a transmission line 
detector~\cite{stripline_jan,gream_2016} using inexpensive 
printed circuit board (PCB) technology. A modular design ensures that detectors of 
different geometry and size can be easily exchanged. 
The NMR detector (including the tuning and matching circuit) is connected to the probe 
skeleton through detachable connectors. Modularity of the probe not only allows 
fast optimisation of the detector but also facilitates the use of dedicated detectors 
for different microfluidic devices on a single probe base. 
Once thw probe base is in place, additional detectors can be manufactured 
within 2-3 days for less than $\sim$200 $\geneuro$. 
The probe is designed for proton detected double resonance. 
The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or 
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials 
such as aluminium profiles of standard size, with only a small number of 
custom-machined parts holding the structure together. 
Detailed construction drawings for the probe are provided in the supporting 
information, and a complete set of CAD files is available for download at [...].
The planar geometry of the detector accommodates exchangeable microfluidic devices 
which can be designed freely for specific experimental requirements as long as the 
overall shape of the device is maintained.

In the remainder of this paper, we discuss the probe design in more detail, 
and characterise its performance in terms of sensitivity and resolution. 
We also demonstrate its application in microfluidic cell culture, 
protein NMR spectroscopy, and micro-imaging. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png} 
\caption{The probe with and without sleeve.}
\label{fig:probe} 
\end{figure}
The probe assembly design is based on readily and easily available materials and parts 
with minimal need for customised fabrication.
All mechanical and electronic components are readily available from commercial sources, 
with the exception of a small number of precision-machined parts which are used 
to hold the assembly together. These can be ordered from commercial prototvaiyping 
manufacturers or machined in-house if mechanical workshop facilities are available.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
\caption{Exploded view of he probe design (left) and assembled probe (right). 
Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a 
generic mounting point for the NMR detector assembly(red). 
A microfluidic device (1) can be inserted from the top of the probe. 
The device is held in place by a spacer (4) between the detector planes (3 and 5) 
ensuring alignment of the sample chamber with the sensitive area on the PCB planes. 
The X channel frequency is controlled by a 
modular PCB insert (6). The modular NMR detector is made up of parts 3 to 6 and is 
connected to the base plate PCB (8) through standard coaxial (SMP) connectors. 
The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10) 
and, auxiliary support disks (12).}
\label{fig:probe-explode} 
\end{figure}

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with 
precision machined parts at either end(scaffold support disks (10)). 
The semi-rigid cables are  threaded through these hollow aluminium tubes 
to reach the detector assembly. 
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly. 
In our case, these were laser cut from 5~mm thick PMMA sheets, 
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 8) is held in place on the top of the probe skeleton by
the detector support rods (9), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permantly fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. It also provides 
capacitors (7) for secondary tuning and matching.
The detector assembly is connected to through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}).
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for 
fine tuning and matching 
at the magnet through tuning rods (13) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular 
axial bore providing access from the bottom of the probe, which can be used for 
temperature and environmental control and/or fluidic connections to the sample as
needed.
The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4) and an 
RF-insert (6). The detector used here is based on a planar transmission line geometry 
as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper 
planes, each with a constriction at the centre.  This geometry gives rise to an 
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field 
and the detection sensitivity
onto the sample area. 
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary 
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs 
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown here) is fixed to the auxiliary disk (2) 
and the scaffold assembly with screws. 
An exchangeable microfluidic device (1) can be inserted from the top of the detector. 
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ. 
The microfluidic device is held in place by the spacer 
between the two PCB planes coinciding the sample chamber with the constriction on the 
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment. 
Since the detector assembly is attached to the probe base through SMP 
connectors, it can easily be exchanged. 
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.
\par
\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. 
A has an O.D. of 44.45 mm, in B, circuit elements of X channel are integrated on the 
PCB itself making it compact (38 mm O.D.). Detachable SMP connectors (14) are used to 
connect the RF insert (6) and the detector assembly. }
\label{fig:ProbePhoto}
\end{figure}
\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) 
for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. 
However, in (B) the circuitry of the RF insert (6) is integrated on the PCB plane (5), 
making the design more compact.
 Probe (A) is compatible with a Varian 600 ultra ) of
shield 14.1 T magnet, with anouter diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an 
outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a 
Bruker narrow bore shim stack. 
Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with 
wide bore magnets with spacers or gradient stack to keep the probe centred.

Microfluidic devices are made from thermally bonded PMMA sheets as described in detail elsewhere. [REF]
Briefly, the devices consist of a 0.5~mm thick middle layer between a top- and bottom layer of 
0.2~mm thickness each. The sample chamber and fluidic network are cut into the middle layer.
The fluidic network on the device can be designed freely as long as the overall shape of the
device is preserved, and the location of the sample chamber is maintained.

@@

The precise dimensions of the detector were optimised for a given sample volume using 
finite element calculations in COMSOL, as described in \cite{gream_2016}. 
The RF response of the probe circuit was simulated using a symbolic  
network analysis code~\cite{gream-thesis} in order to estimate appropriate component values. Final tuning
was done by trial and error using an Agilent FieldFox 4 GHz network analyser. 
PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) 
for manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited resolution to about 10 Hz.
A high-quality Teflon-based RF PCB material (RO3035, Rogers Corp., USA) was therefore used for optimal 
performance in both sensitivity and resolution (\fig{fig:ProbePhoto}(B)).
The probe skeleton was assembled from prefabricated aluminium tubes with the  precision-machined scaffold
disks using brass screws. Semi-rigid transmission lines were then threaded through the tubes, and the TMPCB plate was 
soldered on top. The detector planes (3 and 5) and the PMMA spacer between them were assembled using short bits
of 0.5~mm magnet wire, which were soldered to the appropriate pads in the four corners of the detector structure.

NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 ultra shield 14.1 T magnet.  
Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T 
magnet. 
Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich,UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par

Precision-cut murine liver slices (PCLS) were obtained by first extracting a tissue core of 8 mm diameter 
using a biopsy punch. PCLS of 250-300 $\mu$m thickness were cut from the core using a Krumdieck Tissue slicer, 
and then reduced to 3~mm diameter using a smaller punch.The slices were incubated in well-plates at 37$^\circ$C and 80\%
O\textsubscript{2}, 4\% CO\textsubscript{2}
for 2 hours before imaging.

@@

%\begin{itemize}
%	\item Tuning/matching/channel separation
%	\item tuning range (different field strengths)
%	\item Sensitivity calibration
%	\item Resolution
%	\item RF efficiency, B1 homogeneity
%	\item Example spectra to illustrate versatility:
%		\begin{itemize}
%		\item Growth media (1H), cell culture
%		\item Comparison of spectra obtained at 300, 500, 600 MHz
%		\item HSQC (13C, 15N)
%		\item Liver slice image
%		\end{itemize}
%\end{itemize}
The probe is designed for double resonance, with proton-detected experiments in mind. The circuit is optimised
for efficiency and sensitivity at the high-frequency channel, while allowing RF pulses to be applied
at the X frequency as well. As already explained, the X channel tuning frequency can be changed by simply
 exchanging either only a small RF-insert or the complete detector assembly. 
 \fig{fig:tandm} shows the measured reflection and transmission scattering coefficients ($S$-parameters) as a 
 function of frequency for two combinations of 
 proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz), 
 corresponding to the Larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively. 
 The measurements were performed in the pairs of 600 MHz and 60 MHz and 500 MHz and 125 MHz. The loaded $Q$ factors,
 determined from the -3dB points of the reflection curves, are 42, 49, 32, 36 at 600 MHz, 500 MHz, 
 125 MHz and, 60 MHz respectively. The channel separation is better than -15dB at all operating frequencies.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
\caption{
Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 
60 MHz (\textsuperscript{15}N frequency at 14 T) and 125 MHz (\textsuperscript{13}C frequency at  and 11.7 T). 
Probe can be tuned to 2 frequencies at a time, above results were measured in 
pairs of 600 MHz with 60 MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the 
frequencies as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm} 
\end{figure}

Initially, FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
B$_0$ field maps of the sample chamber obtained from gradient echo images using these detectors 
showed inhomogeneities in the B$_0$ field due to the glass fibre rovings in FR4's composite backing (not shown).
To avoid these inhomogeneities and therefore to achieve better resolution, 
detectors were made from RO3035 material. While RO3035 provides better resolution, it is more expensive 
and takes longer to obtain compared to FR4. 
It therefore makes sense to first prototype new detector designs in FR4, and only use the more expensive RO3035 
once the design has been validated.

\fig{fig:1H-nutation} shows the $^1$H nutation diagram of the water peak in an aqueous solution of 
100~mM $^{15}$N-urea  measured at 600~MHz. The RF field shows good homogeneity, with a 810$^{\circ}$/90$^{\circ}$ 
ratio of more than 90\%. The probe generates 100~kHz nutation frequency from 100~W input power both at 
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$. 
The detector geometry has been optimised for a sample volume of 5~$\mu$l. It compares reasonably well to
the value of 22 kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for single-frequency detector 
of half this size at a Larmor frequency of 300~MHz.

The probe is not sensitive enough to make direct detection of $^{15}$N signals practical. Nutation at the
$^{15}$N frequency was therefore detected indirectly using coherence transfer to protons \cite{bax_indirect}. 
\fig{fig:15N-nutation} shows the results. Using 100~W of input power \todo{verify power setting} 
produces nutation frequencies of 6 kHz for $^{15}$N and 14 kHz for $^{13}$C. 
No signs of arcing were obseved at this power level for pulses up to 1~ms duration.

>>>>

Microfluidic NMR (Nuclear Magnetic Resonance) can probe chemical or bio-chemical reactions, including the metabolism of cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment. We present a dual-channel modular probe assembly for  high efficiency microfluidic-NMR. The samples are contained in exchangeable, flow compatible planar microfluidic devices. The detector including the tuning and matching circuitry of the probe is modular and allows the use of different detectors optimised for different experimental conditions on the same probe base. The complete probe can be built from easily available parts. The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit board) materials. The probe has a limit of detection of 1.4 nmol s$^{-1/2}$, resolution of 3.35 Hz and, an excellent B$_{1}$ homogeneity. The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel (\textsuperscript{13}C or \textsuperscript{15}N) frequencies. We have successfully acquired \textsuperscript{1}H-\textsuperscript{13}C and \textsuperscript{1}H-\textsuperscript{15}N heteronuclear correlation spectrum (HSQC). Particularly, \textsuperscript{1}H-\textsuperscript{15}N HSQC spectrum of 1 mM \textsuperscript{15}N labeled ubiquitin from 2.5 $\mu$l of sample volume.

@@

in the culture of cells, cell aggregates, and small organisms~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}. 

@@

throughput by parallelisation. 

@@

NMR spectroscopy can provide a useful complementary readout capability 
for microfluidic devices. For example, the metabolic activity of cell cultures 
can be followed non-invasively by NMR throughout the course of the experiment~\cite{cellnmr-2015}, 
while effects on cell differentiation can still be analysed by a (destructive) 
transcriptomic analysis at the end. Unfortunately, the sensitivity 
of NMR is much lower than that of optical techniques. 
The small volumes involved in microfluidic systems
 (typically in the range of 1~$\mu$l) 
compound this problem. As is well known, the mass limit of detection of 
inductive NMR detectors improves as they are scaled down~\cite{Olson1995}. 
On this basis, a number of different micro-NMR detector designs have been 
proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. 
In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, 
planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline 
detectors~\cite{stripline_jan}. 
Significant research has gone into developing micro-NMR detectors for flow probes, 
where the sample container takes the form of a fixed capillary into which the sample
must be injected. Only a few designs that allow insertion of a removable microfluidic 
device into the detector have been described~\cite{Spengler-2014,Spengler-2016,gream_2016}.

In this paper we present a novel modular probe designed for generic 
microfluidic-NMR experiments. The design is based on a transmission line 
detector~\cite{stripline_jan,gream_2016} using inexpensive 
printed circuit board (PCB) technology. A modular design ensures that detectors of 
different geometry and size can be easily exchanged. 
The NMR detector (including the tuning and matching circuit) is connected to the probe 
skeleton through detachable connectors. Modularity of the probe not only allows 
fast optimisation of the detector but also facilitates the use of dedicated detectors 
for different microfluidic devices on a single probe base. 
Once the probe base is in place, additional detectors can be manufactured 
within 2-3 days for less than $\sim$200 $\geneuro$. 
The probe is designed for proton detected double resonance. 
The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or 
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials 
such as aluminium profiles of standard size, with only a small number of 
custom-machined parts holding the structure together. 
Detailed construction drawings for the probe are provided in the supporting 
information, and a complete set of CAD files is available for download at \todo{needs to be discussed}.
The planar geometry of the detector accommodates exchangeable microfluidic devices 
which can be designed freely for specific experimental requirements as long as the 
overall shape of the device is maintained.

In the remainder of this paper, we discuss the probe design in more detail, 
and characterise its performance in terms of sensitivity and resolution. 
We also demonstrate its application in microfluidic cell culture, 
protein NMR spectroscopy, and micro-imaging. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png} 
\caption{The probe with and without sleeve.}
\label{fig:probe} 
\end{figure}
The probe assembly design is based on readily and easily available materials and parts 
with minimal need for customised fabrication.
All mechanical and electronic components are readily available from commercial sources, 
with the exception of a small number of precision-machined parts which are used 
to hold the assembly together. These can be ordered from commercial prototyping 
manufacturers or machined in-house if mechanical workshop facilities are available.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
\caption{Exploded view of the probe design (left) and assembled probe (right). 
Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 8) provides a 
generic mounting point for the NMR detector assembly (red). 
A microfluidic device (1) can be inserted from the top of the probe. 
The device is held in place by a spacer (4) between the detector planes (3 and 5) 
ensuring alignment of the sample chamber with the sensitive area on the PCB planes. 
The X channel frequency is controlled by a 
modular PCB insert (6). The modular NMR detector is made up of parts 3 to 6 and is 
connected to the TMPCB (8) through standard coaxial (SMP) connectors. 
The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (10) 
and, auxiliary support disks (12).}
\label{fig:probe-explode} 
\end{figure}

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with 
precision machined parts at both ends (scaffold support disks (10)). 
The semi-rigid cables are  threaded through these hollow aluminium tubes 
to reach the detector assembly. 
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly. 
In our case, these were laser cut from 5~mm thick PMMA sheets, 
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 8) is held in place on the top of the probe skeleton by
the detector support rods (9), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permantly fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. It also provides 
capacitors (7) for secondary tuning and matching of the detector.
The detector assembly is connected to the TMPCB through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}).
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for 
fine tuning and matching 
at the magnet through tuning rods (13) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular 
axial bore providing access from the bottom of the probe, which can be used for 
temperature and environmental control and/or fluidic connections to the sample as
needed.
The detector assembly is made up of two PCBs (3 and 5), a spacer between them (4) and an 
RF-insert (6). The detector used here is based on a planar transmission line geometry 
as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper 
planes, each with a constriction at the centre.  This geometry gives rise to an 
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field 
and the detection sensitivity
onto the sample area. 
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary 
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs 
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2) 
and the scaffold assembly with screws. 
An exchangeable microfluidic device (1) can be inserted from the top of the detector. 
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ. 
The microfluidic device is held in place by the spacer 
between the two PCB planes coinciding the sample chamber with the constriction on the 
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment. 
Since the detector assembly is attached to the probe base through SMP 
connectors, it can easily be exchanged. 
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.

\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (6) for X channel. 
O.D. of A is 44.45 mm and B is 38 mm. Circuit elements of X channel are integrated on the 
PCB in B making it compact. Detachable SMP connectors (14) are used to 
connect the RF insert (6) and the detector assembly.}
\label{fig:ProbePhoto}
\end{figure}
\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) 
for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. 
However, in (B) the circuitry of the RF insert (6) is integrated on the PCB plane (5), 
making the design more compact.
 Probe (A) is compatible with a Varian 600 Premium shielded 14.1 T magnet, with an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an 
O.D. of 38 mm including the sheath, is designed to fit inside a 
Bruker narrow bore shim stack. 
Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with 
wide bore magnets with spacers or gradient stack to keep the probe centred.

Microfluidic devices are made from thermally bonding PMMA sheets.
Briefly, the devices consist of a 0.5~mm thick middle layer between a top and bottom layer of 
0.2~mm thickness each. The sample chamber and fluidic network are cut into the middle layer.
The fluidic network on the device can be designed freely as long as the overall shape of the
device is preserved, and the location of the sample chamber is maintained.

@@

The precise dimensions of the detector were optimised for a given sample volume using 
finite element calculations in COMSOL, as described in \cite{gream_2016}. 
The RF response of the probe circuit was simulated using a symbolic  
network analysis code~\cite{gream-thesis} in order to estimate appropriate component values. Final tuning
was done by trial and error using an Agilent FieldFox 4 GHz network analyser. 
PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) 
for manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited resolution to about 10 Hz.
A high-quality Teflon-based RF PCB material (RO3035, Rogers Corp., USA) was therefore used for optimal 
performance in both sensitivity and resolution (\fig{fig:ProbePhoto}(B)).
The probe skeleton was assembled from prefabricated aluminium tubes held with the precision-machined scaffold
disks using brass screws. Semi-rigid transmission lines were then threaded through the tubes, and the TMPCB plate was 
soldered on top. The detector planes (3 and 5) and the PMMA spacer between them were assembled using short bits
of 0.5~mm magnet wire, which were soldered to the appropriate pads in the four corners of the detector structure.

NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 premium shielded 14.1 T magnet.  
Imaging experiments were performed on Bruker AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T 
magnet. 
Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.

Precision-cut murine liver slices (PCLS) were obtained by first extracting a tissue core of 8 mm diameter 
using a biopsy punch. PCLS of 250-300 $\mu$m thickness were cut from the core using a Krumdieck Tissue slicer, 
and then reduced to 3~mm diameter using a smaller punch. The slices were incubated in well-plates at 37$^\circ$C and 80\%
O\textsubscript{2}, 5\% CO\textsubscript{2}
for 2 hours before imaging.

@@

%\begin{itemize}
%	\item Tuning/matching/channel separation
%	\item tuning range (different field strengths)
%	\item Sensitivity calibration
%	\item Resolution
%	\item RF efficiency, B1 homogeneity
%	\item Example spectra to illustrate versatility:
%		\begin{itemize}
%		\item Growth media (1H), cell culture
%		\item Comparison of spectra obtained at 300, 500, 600 MHz
%		\item HSQC (13C, 15N)
%		\item Liver slice image
%		\end{itemize}
%\end{itemize}
The probe is designed for double resonance, with proton-detected experiments in mind. The circuit is optimised
for efficiency and sensitivity at the high-frequency channel, while allowing RF pulses to be applied
at the X frequency as well. As already explained, the X channel tuning frequency can be changed by simply
 exchanging either only a small RF-insert or the complete detector assembly. 
 \fig{fig:tandm} shows the measured reflection and transmission scattering coefficients ($S$-parameters) as a 
 function of frequency for two combinations of 
 proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz), 
 corresponding to the Larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14.1 T and 11.7 T respectively. 
 The measurements were performed in the pairs of 600 MHz and 60 MHz and 500 MHz and 125 MHz. The loaded $Q$ factors,
 determined from the -3dB points of the reflection curves, are 42, 49, 32, 36 at 600 MHz, 500 MHz, 
 125 MHz and, 60 MHz respectively. The channel separation is better than -15dB at all operating frequencies.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 
\caption{
Experimental tuning and matching curves measured at 600 MHz, 500 MHz, 
60 MHz (\textsuperscript{15}N frequency at 14.1 T) and 125 MHz (\textsuperscript{13}C frequency at  and 11.7 T). 
Probe can be tuned to 2 frequencies at a time, above results were measured in 
pairs of 600 MHz with 60 MHz and 500 MHz with 125 MHz. Decoupling can be performed at all the 
frequencies as the channel separation is better than 15 decibels at all frequencies.}
\label{fig:tandm} 
\end{figure}
Initially, FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
Inhomogeneities in the B$_0$ field due to the glass fibre rovings in FR4's composite backing can be seen as fringes in~\fig{fig:field map} (A). B$_{0}$ field maps of the sample chamber were constructed from 2 gradient echo (FLASH) images having echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms for both FR4 and RO3035 PCB materials with the same chip~(\fig{fig:field map}). The brightness of each pixel is proportional to the sum of the magnitude of the two images, whereas the colour encode the phase difference between them. The full colour range from red to blue spans phase differences from $-\pi$ to $+\pi$.

To avoid the inhomogeneities of FR4 and therefore to achieve better resolution, 
detectors were made from RO3035 material. While RO3035 provides better resolution, it is more expensive 
and takes longer to obtain compared to FR4. 
It therefore makes sense to first prototype new detector designs in FR4, and only use the more expensive RO3035 
once the design has been validated.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png} 
\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and Rogers RO3035 (B) PCB material. Both the field maps were constructed from 2 gradient echo images acquired on a chip filled with 130 mM sodium acetate dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
\label{fig:field map} 
\end{figure}

The RF field at proton frequency shows excellent homogeneity, with a 810$^{\circ}$/90$^{\circ}$ 
ratio of more than 90\% measured from $^1$H nutation of the water peak in an aqueous solution of 
100~mM $^{15}$N-urea at 600~MHz. The probe generates 100~kHz nutation frequency from 100~W input power both at 
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$. 
The detector geometry has been optimised for a sample volume of 5~$\mu$l. It compares reasonably well to
the value of 22 kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for single-frequency detector 
of half this size at a Larmor frequency of 300~MHz. 
For X channel, 100~W of input power 
produces nutation frequencies of 6 kHz for $^{15}$N and 14 kHz for $^{13}$C. 
No signs of arcing were obseved at this power level for pulses up to 1~ms duration.
